Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-03-21 manuscript/manuscript.tex

@@

The code is implemented in Python language,
by using the NumPy and SciPy libraries \citep{vanderwalt2011},
as part of the open-source source library
Fatiando a Terra \citep{uieda2013}.
Our code is very modular and has a
test suite formed by a considerable number of 
assertions, unit tests, doc tests and integration tests.
For readers interested in automated code testing,
we recommend the freely reusable lessons of the Software Carpentry 
(\url{https://software-carpentry.org/}) and at the
description of the doctest module available
in the documentation for Python 2.X 
(\url{https://docs.python.org/2/library/doctest.html}).

The numerical simulations presented here was generated with
the Jupyter Notebook
(\url{http://jupyter-notebook.readthedocs.io/en/latest/notebook.html}),
which is a web application that allows creating and sharing
documents that contain live code, equations, visualizations and
explanatory text.
Besides using the Fatiando a Terra \citep{uieda2013},
the numerical simulations use the 
NumPy library \citep{vanderwalt2011} to perform numerical
computations, the Matplotlib library \citep{hunter2007} to plot
the results and generate figures.
The Jupyter Notebooks used to reproduce all the results presented here
are available at a repository in the GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).

@@

The current version of our code is freely distributed, under 
BSD 3-clause licence, in a repository of GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
The code was developed as part of the Fatiando a Terra 
\citep{uieda2013}, which is an open-source Python 
library for modelling and inversion in geophysics.
Instructions for running the current version of our code
in the Fatiando a Terra are provided at its repository
in GitHub.
Documentation and installation instructions for 
the most current release version of Fatiando a Terra 
are provided at \url http://www.fatiando.org.

>>>>

\usepackage{url}

@@

The code is implemented in the Python language,
by using the NumPy and SciPy libraries \citep{vanderwalt2011},
as part of the open-source source library
Fatiando a Terra \citep{uieda2013}.
Our code is very modular and has a
test suite formed by a considerable number of
assertions, unit tests, doc tests, and integration tests.
We refer the readers interested in best practices for scientific computing to
\citet{wilson2014}.

The numerical simulations presented here were generated with
the Jupyter Notebook
(\url{http://jupyter.org}),
which is a web application that allows creating and sharing
documents that contain live code, equations, visualizations and
explanatory text.
Besides using Fatiando a Terra \citep{uieda2013},
the numerical simulations use the
NumPy library \citep{vanderwalt2011} to perform numerical
computations and the Matplotlib library \citep{hunter2007} to plot
the results and generate figures.
The Jupyter Notebooks used to produce all the results presented here
are available in a repository on GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).

@@

The current version of our code is freely distributed, under the
BSD 3-clause licence, in a repository on GitHub
(\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
Instructions for running the current version of our code
are also provided in the repository.
The code was developed as part of the Fatiando a Terra
\citep{uieda2013} open-source Python
library for modelling and inversion in geophysics.
Documentation and installation instructions for
the 0.5 release version of Fatiando a Terra
are provided at \url{http://www.fatiando.org/v0.5}.
